### 2015-02-08 src/paper4/p4_methods.tex
Fixed units.

Participants were seated on a motorized linear sled with their body and head restrained such that the inter-aural axis aligned with the motion axis. The sled laterally translated participants following a minimum jerk profile of fixed duration (1s) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Auditory cues were suppressed using white noise presented through in-ear head-phones. Experiments were conducted in complete darkness except for visual fixation points, projected by body- or world-fixed laser pointers on a black bar, either 50 or 200 \si{\centi\metre} in front of the sled and at eye level. Eye movements were recorded at 500Hz using an EyeLink II (SR Research, Kanata, Canada) system. Eye position was calibrated before each session using 11 evenly spaced calibration points ranging from -22 to 22 degrees.

@@

We used a two-alternative forced choice (2-AFC) task to study the influence of fixation depth on the perception of linear translation. We tested two fixation depths: near (50 cm) and far (200 \si{\centi\metre}) and two different eye fixation conditions: world-, and body-fixed fixation. A trial contained two sequential motion intervals of equal duration (1s), with the motion in the same direction (either leftward or rightward).

@@

The timing of a single trial is shown in \figref{p4:fig1}A. Each trial started with the onset of a central fixation point (i.e. aligned between the eyes) for 0.5s. Subsequently, the first 1s motion interval commenced, during which the fixation type which was at on the two depths, remained stationary (world condition) or moved along with the participant (body condition). Subsequently a 1.75s delay followed in which the participant was kept in stationary complete darkness. Then, the central fixation point reappeared, followed 0.5 \si{\second} later by a second 1 \si{\second} translation interval, with the same fixation condition but with the fixation point at the other depth as in the first interval. Finally, the participant responded by moving a 1-dimensional joystick away from (longer) or towards (shorter) the body. Top-view illustrations of body-centered and world-centered trials are shown in \figref{p4:fig1} panels B and C.

>>>>

Participants were seated on a motorized linear sled with their body and head restrained such that the inter-aural axis aligned with the motion axis. The sled laterally translated participants following a minimum jerk profile of fixed duration (1 \si{\second}) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Auditory cues were suppressed using white noise presented through in-ear head-phones. Experiments were conducted in complete darkness except for visual fixation points, projected by body- or world-fixed laser pointers on a black bar, either 50 or 200 \si{\centi\metre} in front of the sled and at eye level. Eye movements were recorded at 500Hz using an EyeLink II (SR Research, Kanata, Canada) system. Eye position was calibrated before each session using 11 evenly spaced calibration points ranging from -22 to 22 degrees.

@@

We used a two-alternative forced choice (2-AFC) task to study the influence of fixation depth on the perception of linear translation. We tested two fixation depths: near (50 \si{\centi\metre}) and far (200 \si{\centi\metre}) and two different eye fixation conditions: world-, and body-fixed fixation. A trial contained two sequential motion intervals of equal duration (1 \si{\second}), with the motion in the same direction (either leftward or rightward).

@@

The timing of a single trial is shown in \figref{p4:fig1}A. Each trial started with the onset of a central fixation point (i.e. aligned between the eyes) for 0.5 \si{\second}. Subsequently, the first 1s motion interval commenced, during which the fixation type which was at on the two depths, remained stationary (world condition) or moved along with the participant (body condition). Subsequently a 1.75 \si{\second} delay followed in which the participant was kept in stationary complete darkness. Then, the central fixation point reappeared, followed 0.5 \si{\second} later by a second 1 \si{\second} translation interval, with the same fixation condition but with the fixation point at the other depth as in the first interval. Finally, the participant responded by moving a 1-dimensional joystick away from (longer) or towards (shorter) the body. Top-view illustrations of body-centered and world-centered trials are shown in \figref{p4:fig1} panels B and C.
